\documentclass[a4paper]{article} 
\title{'AYURVED' an ancient science beyond the reach of modern Science} 
\author{Submitted by Dagesh kumar verma} 
\date{6 August 2021} \begin{document} 
\maketitle 
\section{FACT}Artificial intelligence is a branch of the philosophy of technology that explores artificial intelligence and its implications for knowledge and understanding of intelligence, ethics, consciousness, and free will. some scholars argue that the AI community’s dismissal of philosophy is detrimental. The philosophy of artificial intelligence attempts to answer such questions as follows: Can a machine act intelligently? CAN IT SOLVE ANY PROBLEM that a person would solve by thinking? Are human intelligence and machine intelligence the same?Is the human brain essentially a computer? Can machines have a mind, mental states, and consciousness in the same sense that a human being can? Can they feel how things are? Pseudoscience consists of statements, beliefs, or practices that claim to be both scientific and factual but are incompatible with the scientific method.A technique like ayurved is known as pseudoscience it means it is not more than a belief, if this is only a belief than how patients get cured by ayurvedic treatment and patients of non curable diseases also gets cured by ayurved treatment, So how it is happening Just because of belief. It seems we should laugh on the characterised this treatment technique as pseudoscience.Actually the medicines of ayurved is based on the phytochemicals present on the natural things which is always trees say leaf,bark,root of tree and using these things in such a way that only those phyto chemical will be left on the medicine for that particular disease. Can be elaborated more.Ayurved connects human kind from nature in the way that, if one is having heart disease which is Coronay Artery Blockage then if the patient will use the Extrct of Arjun tree bark as tea and take pomegranate juice in regular basis in empty stomach then patient's blockage will start reducing and digestion will also gets stronger. In this way if one get benifited then patient will plant Arjun tree as this tree is a medicine for the patient and he knows if these trees were not left ofr gets extinct the patient will suffer the most.So, none of the ancient science is just a belief or psedoscience it is completely researched and proved that's why these are giving result, The actual fault is in modern science which don't have the ability to understand that. 
\end{document}
